---
title: "Assignment2"
author: "Yakoob Ibrahim"
date: "1/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 1: formatting RMarkdown document
*Yakoob Ibrahim*
## ID-S4655065 
<hr style="border:3px solid rgb(0.9,0.1,0.2,0.9)"> </hr>
# Assignment 2
<hr style="border:3px solid rgb(0.9,0.1,0.2,0.9)"> </hr>
### Part 2: Data Wrangling and visualization 

```{r}
library(tidyverse)
library(skimr)
dataset_meal <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```
### Question1
```{r}
knitr::kable(head(dataset_meal[, 1:5],10))
```

### Question2
```{r}
skim(dataset_meal)
```
### Question3
```{r}
family_income<-fct_reorder(dataset_meal$family_income, dataset_meal$family_income, min)
```
### Question 4
```{r}
nrow(subset(dataset_meal, celebrate=='Yes'))
```
### Question5
```{r}
knitr::kable(dataset_meal %>% group_by(main_dish) %>%  count(main_prep) %>% arrange(desc(n)) %>% head(n=10))
```
### Question6
```{r}
dataset_meal %>% ggplot() +  aes(x = main_dish, fill = main_dish) +   geom_bar() + labs(x = "Main Dish", y = "Count", title = "Main dish served and the method", subtitle = "Main Dish", caption = "main dish served and the method",  fill = "Legend")
```
<p>The graph shows all the main dishes that are prepared and served. The highest served dish is Turkey. It means people like to have the Turkey dish most in almost all the restrurents</p>
<br>
### Question7
```{r}
nrow(subset(dataset_meal, cranberry=='Canned' | cranberry=='Homemade'))
nrow(subset(dataset_meal, gravy=='Yes'))
```

### Question8 and 9
```{r}
knitr::kable(dataset_meal %>% group_by(celebrate) %>%  count(family_income) %>% arrange(desc(n)) %>% head(n=10))
```
```{r}
dataset_meal %>% ggplot() +  aes(x = celebrate, fill =family_income) +   geom_bar() + labs(x = "celebrate", y = "Count", title = "Distribution of those who celebrate across income ranges", subtitle = "Celebrate", caption = "Distribution of those who celebrate across income ranges",  fill = "Legend")
```
<p>The graph shows that there are large number of people who celebrated across different income group. But there are very few people who doesnot celebrate at all. Even there are few people having income level betweer 0 to 9999 also celebrate</p>
<br>
### Question10
```{r}
Array1<-dataset_meal %>% select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
print(Array1)
```
<p>The above mentioned code extract the records having three fields whose values start with specific word. In case of first column the value starts with side, secod column value starts with pie and third starts with dessert</p>
<br>

### Question11 and 12
```{r}
library(widyr)
```
<p>The function pairwise_cor shows the correlation between different set of pairs that are present in the new dataset. The highest corrlation value is between Cookies and Brownies, also lowest correlation between the Mashed potatoes and Pumpkin</p>
<br>
```{r}
Array1 %>% pairwise_cor(value, id, sort = TRUE)
```
<p>The function pairwise_cor shows the correlation between different set of pairs that are present in the new dataset. The highest corrlation value is between Cookies and Brownies, also lowest correlation between the Mashed potatoes and Pumpkin</p>
<br>
 
### Question 13
```{r}
#dataset_meal <- do.call(data.frame, lapply(dataset_meal, function(x) {
#  replace(x, is.infinite(x) | is.na(x) | is.nan(x), 0)
#  })
#)
#simple.fit = lm(main_dish~family_income, data=head(dataset_meal,6))
#summary(simple.fit)
#simple.fit = lm(gender~family_income, data=head(dataset_meal,6))
#summary(simple.fit)
#simple.fit = lm(celebrate~family_income, data=head(dataset_meal,6))
#summary(simple.fit)
```
<p>The linear regression model for the prediction of the family income based on the main_dish ordered, There are three models that are applied, best is in the relation between main_dish and the family income.</p>
<br>


